Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-04-19 intro.tex
2015.04.19 (Vassilis) Adding a recent reference (from 2014).

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing system was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when it topped
$26$ million users sharing over $80$ million songs.
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers, as well as 
{\sl BitTorrent} connecting over $150$ million monthly users by January $2012$~\cite{bittorrentusers}.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers} while on January $21$st, $2013$,
the astonishing figure of $50$ million concurrently-online users
was reported~\cite{skypesymusers}.
%%
Apart from the above, a startling number of diverse and successful
applications have been built based on \p\ architectures. Some of them include:
distributed search engines~\cite{yaci}, 
distributed data-storage systems~\cite{kbc_oceanstore_2000,bdet_fsdfs_2000,dkkms_cfs_2001,dr_pastutility_2001,abc_farsite_2002,mmfc_ivy_2002,arla,agebh_dks_2003},
Web caches, archives and publishing systems~\cite{ird_squirrel_2002,bags_youserv_2002,wrc_publius_2000,wm_tangler_2001},
messaging and dissemination applications~\cite{threedegrees,icpp08-pd}, 
event-notification infrastructures~\cite{rkcd_scribe_2001,cdkr_scribe_2002,agebh_dks_2003}, 
naming services~\cite{cmm_chorddns_2002}, 
censor-resistant stores~\cite{cswh_freenet_2001} and
lately, even cloud-based platforms~\cite{mgpj_cloudsnap_2011}.

>>>>

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing system was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when it topped
$26$ million users sharing over $80$ million songs.
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers, as well as 
{\sl BitTorrent} connecting over $150$ million monthly users by January $2012$~\cite{bittorrentusers}.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers}, an astonishing $50$+ million concurrently-online
users since 2013~\cite{skypesymusers} and an ever-growing Skype-to-Skype traffic
recently estimated to 214 billion minutes~\cite{skypetraffic}.

%%
Apart from the above, a startling number of diverse and successful
applications have been built based on \p\ architectures. Some of them include:
distributed search engines~\cite{yaci}, 
distributed data-storage systems~\cite{kbc_oceanstore_2000,bdet_fsdfs_2000,dkkms_cfs_2001,dr_pastutility_2001,abc_farsite_2002,mmfc_ivy_2002,arla,agebh_dks_2003},
Web caches, archives and publishing systems~\cite{ird_squirrel_2002,bags_youserv_2002,wrc_publius_2000,wm_tangler_2001},
messaging and dissemination applications~\cite{threedegrees,icpp08-pd}, 
event-notification infrastructures~\cite{rkcd_scribe_2001,cdkr_scribe_2002,agebh_dks_2003}, 
naming services~\cite{cmm_chorddns_2002}, 
censor-resistant stores~\cite{cswh_freenet_2001} and
lately, even cloud-based platforms~\cite{mgpj_cloudsnap_2011}.
